Quality Definitions of Qualities

### 2019-12-18 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Minor edits
fixed errors

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked with pdf}
\end{defn}

@@

\begin{defn}
 The capability of the software product to maintain a specified level of performance when used under specified conditions \cite{ISO9126}.
\end{defn}

\begin{defn} \label{reliabilitySelected1} 
	It is the probability of failure-free operation of a computer program in a specified environment for a specified time
    \citep{musa1987software}.
\end{defn}

>>>>

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked with pdf} \wss{Great!  Did you add the Mccall paper to the pub repo?}
\oo{I will}
\end{defn}

@@

\begin{defn}
 The capability of the software product to maintain a specified level of performance when used under specified conditions \cite{ISO9126}.
\end{defn}
\begin{defn} \label{reliabilitySelected1} It is the probability of failure-free
  operation of a computer program in a specified environment for a specified
  time \citep{musa1987software}.
\end{defn}
